---
title: "q3"
author: "Zexuan Fang"
date: "03/10/2019"
output: pdf_document
---

# Q3. 
## Yield on transfers for profit signature in Q(2)-a was found to be 0.473827, thus 47%. 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
yield.on.transfer.2 <- function(i){
  sum(profit.signature.2/(1+i)^(1:10))
}
irr.2 <- uniroot(yield.on.transfer.2, c(0,1))$root
cbind(irr.2)
```

### To calculate the profit signature, expected present value of transfer and the yield on transfer for this policy, we started by firstly determining the changes to fees and rates resulting from the setting of policy, as shown below table, 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#changes resulting from inclusion of insurance cover
insurance.cover <- 20000 
insurance.charge <- 1.2*(q_d) 
new.maintenance.expense <- c(75, 75*1.25^(1:9))

#expect insurance charge.BoY
expect.insurance.charge <- c(insurance.cover*insurance.charge[1],
                             insurance.cover*insurance.charge[2:10]*(al_x[2:10]/al_x[1]))

#new total expense.BoY
new.expense.total <- c(acquisition.expense+new.maintenance.expense[1],
                       new.maintenance.expense[2:10] )
 
new.expect.expense.total <- c(new.expense.total[1], 
                              new.expense.total[2:10]*(al_x[2:10]/al_x[1]))

insurance.charge.fee <- insurance.cover*insurance.charge
cbind(insurance.cover, insurance.charge.fee, new.maintenance.expense,
      new.expense.total, new.expect.expense.total)
```

### Thus, resulting from the above fees change, we calculated the remaining new amounts for various other columns, which include some from the unit fund such as buy sell margin fees, investe premium, value of units, transfers to non-unit fund, and others from non-unit fund such as death benefit, surrender benefit, interest on non-unit fund. Amounts are summarised in the below table. 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#new buy sell margin fee 
new.buy.sell.fee <- buy.sell.margin*(premium.10.year-premium.fee)
#new invested premium.BoY
new.invested.premium <- premium.10.year - 
  premium.fee - new.buy.sell.fee-insurance.cover*insurance.charge


new.expect.invested.premium <- c(new.invested.premium[1],
                                 new.invested.premium[2:10]*(al_x[2:10]/al_x[1]))

#new value of units.EoY
new.value.of.units <- rep(0, 10)
new.value.of.units[1] <- new.invested.premium[1]*(1+unit.fund.earn)*(1-asset.fee.charge)
for (i in 2:10) {
  new.value.of.units[i] <- (new.value.of.units[i-1]+
                              new.invested.premium[i])*(1+unit.fund.earn)*(1-asset.fee.charge)
}

new.expect.value.of.units <- new.value.of.units*(al_x[2:11]/al_x[1])

#adjusted death benefit.EoY
new.death.benefit <- rep(insurance.cover,10) + new.value.of.units

new.expect.death.benefit <- new.death.benefit*(ad_d/al_x[1])

#new surrender benefit 
new.surrender.benefit <- new.value.of.units

new.expect.surrender.benefit <- new.surrender.benefit*(ad_w/al_x[1])

#new interest in unit fund.EoY
new.interest.unit.fund <- rep(0,10)
new.interest.unit.fund[1] <- new.expect.invested.premium[1]*unit.fund.earn
for (i in 2:10) {
  new.interest.unit.fund[i] <- unit.fund.earn*(new.expect.value.of.units[i-1]+
                                                 new.expect.invested.premium[i])
}

#new transfers to non-unit.EoY
new.transfer.to.non.unit <- new.expect.invested.premium + new.interest.unit.fund +
  c(0, new.expect.value.of.units[1:9]) - new.expect.value.of.units

#new interest on non-unit.EoY
new.interest.non.unit.fund <- non.uni.fund.earn*(expect.premium.fee+
                                               expect.buy.sell.fee +
                                              expect.insurance.charge-
                                              new.expect.expense.total)

#new expect buy-sell fee
new.expect.buy.sell.fee <- new.buy.sell.fee*(al_x[1:10]/al_x[1])

cbind(new.buy.sell.fee, new.invested.premium, new.value.of.units, 
      new.transfer.to.non.unit, new.death.benefit, new.surrender.benefit,
      new.expect.buy.sell.fee, new.expect.invested.premium, new.expect.value.of.units, 
      new.expect.death.benefit, new.expect.surrender.benefit)

```


### Thus, from the above values, we calculated the required values as shown in the below table. 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#new profit signature 
new.profit.signature <- expect.premium.fee + new.expect.buy.sell.fee +
  expect.insurance.charge +new.interest.non.unit.fund + new.transfer.to.non.unit -
  new.expect.expense.total - new.expect.death.benefit - new.expect.surrender.benefit


yield.on.transfer.3 <- function(i){
  sum(new.profit.signature/(1+i)^(1:10))
}

irr3 <- uniroot(yield.on.transfer.3,c(-2, 1))$root

irr.3 <- c(rep(0,9), irr3)

EPV.profit.signature.3 <- sum(new.profit.signature*valuation.v.2)

EPV.3 <- c(rep(0,9), EPV.profit.signature.3)

cbind(new.profit.signature, EPV.3, irr.3)
```